Fixing Vulnerabilities Hinders Maintainability

### 2019-02-06 paper/ICPC19/icpc19.tex
small fixes

\lstdefinestyle{PHPStyle} {
    language=PHP,
    alsolanguage=HTML,
    backgroundcolor=\color{white},   % choose the background color
    basicstyle=\ttfamily\scriptsize,        % size of fonts used for the code
    breaklines=true,                 % automatic line breaking only at whitespace
    captionpos=b,                    % sets the caption-position to bottom
    commentstyle=\color{mygray}\bfseries,    % comment style
    escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
    keywordstyle=\color{blue},       % keyword style
    stringstyle=\color{mymauve},     % string literal style
    frame=single,
    stepnumber=1,
    escapeinside={/*!}{!*/},
    moredelim=**[l][\color{mygreen}]{+\ },
    moredelim=*[l][\color{red}]{-\ }
}

>>>>

\lstdefinestyle{PHPStyle} {
    language=PHP,
    alsolanguage=HTML,
    backgroundcolor=\color{white},   % choose the background color
    basicstyle=\ttfamily\scriptsize,        % size of fonts used for the code
    breaklines=true,                 % automatic line breaking only at whitespace
    captionpos=b,                    % sets the caption-position to bottom
    commentstyle=\color{mygray}\bfseries,    % comment style
    escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
    keywordstyle=\color{blue},       % keyword style
    stringstyle=\color{mymauve},     % string literal style
    frame=single,
	numbers=left,
    stepnumber=1,
	xleftmargin=2em,
    escapeinside={/*!}{!*/},
    moredelim=**[l][\color{mygreen}]{+\ },
    moredelim=*[l][\color{red}]{-\ }
}
